What We Eval in the Shadows

### 2021-09-09 paper/main.tex
Align better Table 2 and Table 3
7 + minor changes

\begin{table}[H]
\centering
\small
\begin{tabular}{@{}l@{\hspace{1.5cm}}l@{}}
\begin{minipage} {5cm}\small
  \begin{tabular}{r@{\,}r@{\,}l@{}r|r@{\,}r@{\,}l@{}r@{}} \toprule
    \multicolumn{3}{c}{\bf \small\#calls} &\bf \small \#pck
&     \multicolumn{3}{c}{\bf \small\#calls} &\bf \small\#pck \\\midrule
\tt 1 &--& \tt 10      & \packageBina  & \tt 10K &--&\tt 100K  & \packageBine\\
\tt 11 &--& \tt 100    & \packageBinb  & \tt 100K &--&\tt 1M  & \packageBinf\\
\tt 101 &--& \tt 1K    & \packageBinc  & \tt 1M &--&\tt 10M   & \packageBing\\
\tt 1K &--& \tt 10K    & \packageBind  & \tt 10M &--& \tt 100M & \packageBinh\\\bottomrule
\end{tabular}\caption{Call frequency}\label{tab:freq}
\end{minipage}
&
\begin{minipage}{7cm}\small
\begin{tabular}{@{}r|r@{~}r@{}r@{~}r@{}}\toprule
  &\eval & \k{evalq} & \k{eval} & \k{local}\\[-1.3mm]
           & & & \k{.parent} &\\[1.3mm]\midrule
\small Static sites &\packageStaticeval&\packageStaticevalq&\packageStaticevalparent&\packageStaticlocal \\
\small Exercised sites&\packageTriggeredeval&\packageTriggeredevalq&\packageTriggeredevalparent&\packageTriggeredlocal\\
\small Invocations&\packageEvalsRnd&\packageEvalqsRnd&\packageEparentsRnd&\packageLocalsRnd\\\bottomrule
\end{tabular}\caption{Variants}\label{tab:variantseval}
\end{minipage}\end{tabular}
\end{table}

@@

\begin{tabular}{@{}p{.97\linewidth}}
  \medskip\EE{$min(e)=\c{\$}$}\\[-2mm]\small This shape extends \k{X} to include lookup
  with the dollar operator, \eg~\k{x\$f}, and vector indexing, \eg~\k{x[42]} and
  \k{x[[24]]}. This takes a few more steps of evaluation on average and is
  typically used in a function environment.
  \\
  \medskip\EE{$min(e)=$~\k{<-}}\\[-2mm]\small This includes both direct assignment {\tt
  <-} and parent environment assignment {\tt <\,\!<-} as well as the \k{assign}
  function. It subsumes \k{\$}. Assignments represent the most obvious source
  of side effects in \eval. Most cases originate from trivial code generation
  where the assign expression is assembled using parse or substitute, often in
  a loop.
  \\
  \medskip\EE{$min(e)=\c{F()}$}\\[-2mm]\small This shape represents function calls without variable lookups or
  assignment. A variable is allowed in the function position; looking up
  functions does not trigger computation unless the function's name
  is bound to a promise. This shape typically does not perform much work.
\end{tabular}

@@

\paragraph{Discussion.} The number of different shapes that any given
\eval site sees is an indication of the versatility of that site.
\packageNbOneMinimizedPercent of sites only see a single expression shape. It
would be encouraging if one could, given a small training set, predict the shape
of \evals to come. In our corpus, only a few sites are highly polymorphic with
more than eight shapes. An example of those is the pipe operator of the
\k{magrittr} package which is used to compose functions, \eg instead of
\k{f(g(h(x),y),z)} one can write \k{h(x) \%>\% g(y) \%>\% f(z)}. As there are many
different patterns of use, there are also many different shapes. In comparison
with R, JavaScript's \eval usage was more straightforward and more predictable,
as reported by \citet{oopsla12b}, with 98\% of sites with only one shape. On the
other hand, there are \packageNbSimpleMinimizedOne sites that only receive one
of the simple shapes (\ie\xspace \k{X}, \k{V}, \k{\$} or \k{<-}), and
\packageNbSimpleMinimizedMore sites get multiple simple shapes. Among these
sites, there are many cases where \eval could be possibly replaced by simpler constructs
such as \k{get} to lookup a name in an environment, \k{assign} to set a value to
a name in an environment, or \k{do.call} to call a function reflectively.

@@

\Eval may perform side-effects. We care about effects that are visible after a
call finishes, \ie variable definitions, updates, and removals. Knowing the
environments in which these side-effects happen can help determine the impact of
\eval on our ability to reason about the code. Our analysis records information
about every environment. From the recorded data, we discard side-effects coming
from unit testing frameworks as they use \eval to run all their tests and thus
dominate the side-effect data.\footnote{The corpus has \k{RUnit, testthat,
    tinytest} and \k{unitizer} testing frameworks.}

@@

\begin{lstlisting}[caption={\k{data.table::[}}, captionpos=b]
> flights[carrier=="DL" & year == 2014, mean(dep_delay), by=origin]
#    origin       V1
# 1:    LGA 11.35083
# 2:    EWR 14.96171
# 3:    JFK 12.45414
\end{lstlisting}\medskip

At its core, the \k{[} operator uses \k{substitute} to capture its operand
expressions, transforms them, and evaluates them using \eval in the given data
frame. We omit the implementation as it spans over 1700 lines at the time of
this writing\footnote{Its implementation can be found at:
  \url{https://github.com/Rdatatable/data.table/blob/master/R/data.table.R}}.

@@

\begin{lstlisting}[caption={\k{glue::glue}}, captionpos=b]
> greeting <- "Hello"
> glue('{greeting} World!')
# Hello World!
\end{lstlisting}\medskip

@@

\begin{lstlisting}[caption={\k{glue::glue_data}}, captionpos=b]
> flights[carrier=="DL" & year == 2014, mean(dep_delay), by=origin] |>
    glue_data("{origin} has average delay of {round(V1)} min")
# LGA has average delay of 11 min
# EWR has average delay of 15 min
# JFK has average delay of 12 min
\end{lstlisting}

@@

% To remove "Listing i" in the captions from this point, as we do not refer to them by number
% We define and refer to listings in 2.2 so we need to put that captionsetup only here
\captionsetup[lstlisting]{labelformat=empty} 
\begin{lstlisting}[caption={\k{AdapSamp::rARS}}, captionpos=b]
 function(n,formula) {
   p <- function(x) eval(parse(text=formula))
   ...
 }
\end{lstlisting}

@@

\begin{lstlisting}[caption={\k{statnet.common::NVL}}, captionpos=b]
 function(...) {
   for (e in eval(substitute(alist(...)))) {
     if (!is.null(eval(e, parent.frame()))) break
   }
   e
 }
\end{lstlisting}

\paragraph{Controlled Evaluation} \Eval can be used to control when and if
expressions are evaluated. For example, \k{assertthat} provides users with the
ability to make assertions and, if they fail, produce legible error messages.
The \k{assertthat::see_if} function accepts a vararg with a list of
expressions. It extracts these expressions using the extracting varargs
pattern and evaluates them sequentially in the caller's environment using
\k{eval}. If an expression does not hold, an error is generated.

\begin{lstlisting}[caption={\k{assertthat::see_if}}, alsoletter={\_}, captionpos=b]
 function(..., env=parent.frame(), msg=NULL) {
   asserts <- eval(substitute(alist(...)))
   for (assertion in asserts) {
     res <- tryCatch({
       eval(assertion, env)
     }, assertError=function(e) { structure(FALSE, msg=e$message) })
   ...
 }
\end{lstlisting}

\paragraph{Shadowing} Some packages use \eval to implement variations of the
\k{base} R functions. For example, the \k{igraph} package provides the
\k{do_call} function shown below. This is a variant of the builtin \k{do.call}
function with different semantics for resolving the function name. It
constructs a call from a name and a list of arguments and passes it to \eval.

\begin{lstlisting}[caption={\k{igraph::do\_call}}, captionpos=b]
 function(f,...,args=list(),env=parent.frame()) {
   f <- substitute(f)
   eval(make_call(f,...,args), env)
 }
\end{lstlisting}

@@

\begin{lstlisting}[caption={\k{Rcpp::.makeCppMethods}}, captionpos=b]
 function(methods, env) {
   for(what in cppMethods)
     methods[[what]] <-
       eval(substitute(function(...)CppObject$what(...)), env)
   ...
 }
\end{lstlisting}

@@

\begin{lstlisting}[caption={\k{survival::survfit.formula}}, captionpos=b]
 function(formula, data, weights, ...) {
   Call <- match.call()
   indx <- match(c('formula', 'data', 'weights'), names(Call), nomatch=0)
   temp <- Call[c(1, indx)]
   temp[[1L]] <- quote(stats::model.frame)
   mf <- eval.parent(temp)
   ...
 }
\end{lstlisting}
\medskip

@@

\begin{lstlisting}[caption={\k{base::write.csv}}, captionpos=b]
 function (...) {
   Call <- match.call(expand.dots = TRUE)
   Call$sep <- ","
   Call$dec <- "."
   Call$qmethod <- "double"
   Call[[1L]] <- as.name("write.table")
   eval.parent(Call)
 }
\end{lstlisting}

@@

\begin{lstlisting}[caption={\k{aibd::scalaEnsure}}, captionpos=b]
 function() {
   env <- parent.env(environment())
   eval(parse(text=paste0('unlockBinding("s", env)')))
   assign("s", s, envir=env)
   lockBinding("s", env)
   ...
 }
\end{lstlisting}\medskip

@@

In R, \eval is used chiefly for meta-programming and accessing remote
environments. Unlike JavaScript, which according to ~\citet{ecoop11} had a small
set of well-defined patterns that could be rewritten without \eval, our results
suggest that \eval is an integral part of programming in R.

The cases where \eval appears to be an overkill include simple expression shapes
such as \k{X}, \k{V}, \k{\$}, \k{<-}, and \k{FUN}. Variable lookup in a remote
environment can be performed by the builtin \k{get} function. A similar case can
be made for assignment and the \k{assign} function. There is a dedicated
\k{do.call} function to perform function calls. However, the unnecessary uses of
\eval are not easy to find and often can only be uncovered by manual analysis.
Dynamic analysis is limited due to coverage issues, and static analysis of R
remains an open problem.

\begin{lstlisting}[caption={Unnecessary use of \eval},label=lst:unnecessary]
 PerformanceAnalytics::chart.QQPlot <- function (d="norm",dp,...) {
   q.f <- eval(parse(text=paste0("q",d)))
   z <- NULL
   eval(parse(text=paste0("z<-q.f(",dp,",...)")))
\end{lstlisting}\medskip

@@

\begin{lstlisting}
 q.f <- get(paste0("q",d))
 z <- q.f(dp, ...)
\end{lstlisting}

Another example, from \k{coin::copyslots}, constructs an expression that accesses
fields of an object and copies them.

\begin{lstlisting}
  eval(str2lang(paste0("target@", s, " <- source@", s)))
\end{lstlisting}

% TODO: show how will it look with symbolic field read and write

This can be replaced by symbolic field reads and writes:

% This should be enough:
\begin{lstlisting}
 slot(target, s) <- slot(source, s)
\end{lstlisting}

We have not yet touched on alternative implementations of \eval. The tidyverse
libraries\footnote{An opinionated collection of R packages designed for data
  science. It consists of some of the most popular packages.} include their own
implementation of \eval called \k{rlang::eval\_tidy}~\cite{tidyverse}, which
departs from \eval in two ways. First, it supports the evaluation of quosures,
custom objects used for metaprogramming that bundle expressions with an
environment. The \k{eval\_tidy} function accepts a data mask argument, a set of
bindings such as a data frame or list, which takes precedence over the
environment. Effects such as assignments happen in the data mask, and
expressions such as \k{return()} do not work since the data mask does not
correspond to a frame on the call stack.

>>>>

\begin{table}[H]
\centering
\small

\begin{tabular}{@{\hspace{0.5cm}}l@{\hspace{1.2cm}}l}
\begin{minipage}{5cm}\small
  \begin{tabular}{r@{\,}r@{\,}l@{}r|r@{\,}r@{\,}l@{}r@{}} \toprule
    \multicolumn{3}{c}{\bf \small\#calls} &\bf \small \#pck
&     \multicolumn{3}{c}{\bf \small\#calls} &\bf \small\#pck \\\midrule
\tt 1 &--& \tt 10      & \packageBina  & \tt 10K &--&\tt 100K  & \packageBine\\
\tt 11 &--& \tt 100    & \packageBinb  & \tt 100K &--&\tt 1M  & \packageBinf\\
\tt 101 &--& \tt 1K    & \packageBinc  & \tt 1M &--&\tt 10M   & \packageBing\\
\tt 1K &--& \tt 10K    & \packageBind  & \tt 10M &--& \tt 100M & \packageBinh\\\bottomrule
\end{tabular}\caption{Call frequency}\label{tab:freq}
\end{minipage}
&
\begin{minipage}{8cm}\small
\begin{tabular}{@{}r|rrrr}\toprule
  &\eval & \k{evalq} & \k{eval} & \k{local}\\[-1.3mm]
           & & & \k{.parent} &\\[1.3mm]\midrule
\small Static sites &\packageStaticeval&\packageStaticevalq&\packageStaticevalparent&\packageStaticlocal \\
\small Exercised sites&\packageTriggeredeval&\packageTriggeredevalq&\packageTriggeredevalparent&\packageTriggeredlocal\\
\small Invocations&\packageEvalsRnd&\packageEvalqsRnd&\packageEparentsRnd&\packageLocalsRnd\\\bottomrule
\end{tabular}\caption{Variants}\label{tab:variantseval}
\end{minipage}\end{tabular}
\end{table}

@@

\begin{tabular}{@{}p{.97\linewidth}}
  \medskip\EE{$min(e)=\c{\$}$}\\[-2mm]\small This shape extends \k{X} to include lookup
  with the dollar operator, \eg~\texttt{x\$f}, and vector indexing, \eg~\k{x[42]} and
  \k{x[[24]]}. This takes a few more steps of evaluation on average and is
  typically used in a function environment.
  \\
  \medskip\EE{$min(e)=$~\k{<-}}\\[-2mm]\small This includes both direct assignment {\tt
  <-} and parent environment assignment {\tt <\,\!<-} as well as the \k{assign}
  function. It subsumes \texttt{\$}. Assignments represent the most obvious source
  of side effects in \eval. Most cases originate from trivial code generation
  where the assign expression is assembled using parse or substitute, often in
  a loop.
  \\
  \medskip\EE{$min(e)=\c{F()}$}\\[-2mm]\small This shape represents function calls without variable lookups or
  assignment. A variable is allowed in the function position; looking up
  functions does not trigger computation unless the function's name
  is bound to a promise. This shape typically does not perform much work.
\end{tabular}

@@

\paragraph{Discussion.} The number of different shapes that any given
\eval site sees is an indication of the versatility of that site.
\packageNbOneMinimizedPercent of sites only see a single expression shape. It
would be encouraging if one could, given a small training set, predict the shape
of \evals to come. In our corpus, only a few sites are highly polymorphic with
more than eight shapes. An example of those is the pipe operator of the
\k{magrittr} package which is used to compose functions, \eg instead of
\k{f(g(h(x),y),z)} one can write \k{h(x) \%>\% g(y) \%>\% f(z)}. As there are many
different patterns of use, there are also many different shapes. In comparison
with R, JavaScript's \eval usage was more straightforward and more predictable,
as reported by \citet{oopsla12b}, with 98\% of sites with only one shape. On the
other hand, there are \packageNbSimpleMinimizedOne sites that only receive one
of the simple shapes (\ie\xspace \k{X}, \k{V}, \texttt{\$} or \k{<-}), and
\packageNbSimpleMinimizedMore sites get multiple simple shapes. Among these
sites, there are many cases where \eval could be possibly replaced by simpler constructs
such as \k{get} to lookup a name in an environment, \k{assign} to set a value to
a name in an environment, or \k{do.call} to call a function reflectively.

@@

\Eval may perform side-effects. We care about effects that are visible after a
call finishes, \ie variable definitions, updates, and removals. Knowing the
environments in which these side-effects happen can help determine the impact of
\eval on our ability to reason about the code. Our analysis records information
about every environment. From the recorded data, we discard side-effects coming
from unit testing frameworks as they use \eval to run all their tests and thus
dominate the side-effect data.\footnote{The corpus has \texttt{\scriptsize RUnit, testthat,
    tinytest} and \texttt{\scriptsize unitizer} testing frameworks.}

@@

\begin{lstlisting}[title={\k{data.table::[}}, captionpos=b]
> flights[carrier=="DL" & year == 2014, mean(dep_delay), by=origin]
#    origin       V1
# 1:    LGA 11.35083
# 2:    EWR 14.96171
# 3:    JFK 12.45414
\end{lstlisting}\medskip

At its core, the \k{[} operator uses \k{substitute} to capture its operand
expressions, transforms them, and evaluates them using \eval in the given data
frame. We omit the implementation as it spans over 1700 lines at the time of
this writing.\footnote{Its implementation can be found at:
  \url{https://github.com/Rdatatable/data.table/blob/master/R/data.table.R}}

@@

\begin{lstlisting}[title={\k{glue::glue}}, captionpos=b]
> greeting <- "Hello"
> glue("{greeting} World!")
# Hello World!
\end{lstlisting}\medskip

@@

\begin{lstlisting}[title={\k{glue::glue_data}}, captionpos=b]
> flights[carrier=="DL" & year == 2014, mean(dep_delay), by=origin] |>
    glue_data("{origin} has average delay of {round(V1)} min")
# LGA has average delay of 11 min
# EWR has average delay of 15 min
# JFK has average delay of 12 min
\end{lstlisting}

@@

% To remove "Listing i" in the captions from this point, as we do not refer to them by number
% We define and refer to listings in 2.2 so we need to put that captionsetup only here
\begin{lstlisting}[title={\k{AdapSamp::rARS}}, captionpos=b]
 function(n,formula) {
   p <- function(x) eval(parse(text=formula))
   ...
 }
\end{lstlisting}

@@

\begin{lstlisting}[title={\k{statnet.common::NVL}}, captionpos=b]
 function(...) {
   for (e in eval(substitute(alist(...)))) {
     if (!is.null(eval(e, parent.frame()))) break
   }
   e
 }
\end{lstlisting}

\paragraph{Controlled Evaluation} \Eval can be used to control when and if
expressions are evaluated. For example, \k{assertthat} provides users with the
ability to make assertions and, if they fail, produce legible error messages.
The \texttt{\small assertthat::see\_if} function accepts a vararg with a list of
expressions. It extracts these expressions using the extracting varargs
pattern and evaluates them sequentially in the caller's environment using
\k{eval}. If an expression does not hold, an error is generated.

\begin{lstlisting}[title={\texttt{\small assertthat::see\_if}}, alsoletter={\_}, captionpos=b]
 function(..., env=parent.frame(), msg=NULL) {
   asserts <- eval(substitute(alist(...)))
   for (assertion in asserts) {
     res <- tryCatch({
       eval(assertion, env)
     }, assertError=function(e) { structure(FALSE, msg=e$message) })
   ...
 }
\end{lstlisting}

\paragraph{Shadowing} Some packages use \eval to implement variations of the
\k{base} R functions. For example, the \k{igraph} package provides the
\k{do_call} function shown below. This is a variant of the built-in \k{do.call}
function with different semantics for resolving the function name. It
constructs a call from a name and a list of arguments and passes it to \eval.

\begin{lstlisting}[title={\k{igraph::do\_call}}, captionpos=b]
 function(f,...,args=list(),env=parent.frame()) {
   f <- substitute(f)
   eval(make_call(f,...,args), env)
 }
\end{lstlisting}

@@

\begin{lstlisting}[title={\k{Rcpp::.makeCppMethods}}, captionpos=b]
 function(methods, env) {
   for(what in cppMethods)
     methods[[what]] <-
       eval(substitute(function(...)CppObject$what(...)), env)
   ...
 }
\end{lstlisting}

@@

\begin{lstlisting}[title={\k{survival::survfit.formula}}, captionpos=b]
 function(formula, data, weights, ...) {
   Call <- match.call()
   indx <- match(c("formula", "data", "weights"), names(Call), nomatch=0)
   temp <- Call[c(1, indx)]
   temp[[1L]] <- quote(stats::model.frame)
   mf <- eval.parent(temp)
   ...
 }
\end{lstlisting}
\medskip

@@

\begin{lstlisting}[title={\k{base::write.csv}}, captionpos=b]
 function (...) {
   Call <- match.call(expand.dots = TRUE)
   Call$sep <- ","
   Call$dec <- "."
   Call$qmethod <- "double"
   Call[[1L]] <- as.name("write.table")
   eval.parent(Call)
 }
\end{lstlisting}

@@

\begin{lstlisting}[title={\k{aibd::scalaEnsure}}, captionpos=b]
 function() {
   env <- parent.env(environment())
   eval(parse(text=paste0('unlockBinding("s", env)')))
   assign("s", s, envir=env)
   lockBinding("s", env)
   ...
 }
\end{lstlisting}\medskip

@@

In R, \eval is used chiefly for meta-programming and accessing remote
environments. Unlike JavaScript, which according to~\citet{ecoop11} had a small
set of well-defined patterns that could be rewritten without \eval, our results
suggest that \eval is an integral part of programming in R. However, there are
cases in which \eval is not needed, and other, more stylized functions could
have been used. There are also alternatives to \eval that provide
a more principled way for meta-programming and dealing with lazy evaluation. In
this section, we briefly discuss these issues.

\paragraph{Unnecessary use of eval} The cases where \eval appears to be an
overkill include simple expression shapes such as \k{X}, \k{V}, \texttt{\$}, \k{<-},
and \k{FUN}. Variable lookup in a remote environment can be performed by the
built-in \k{get} function. A similar case can be made for assignment and the
\k{assign} function. There is a dedicated \k{do.call} function to perform
function calls. However, the unnecessary uses of \eval are not easy to find and
often can only be uncovered by manual analysis. Dynamic analysis is limited due
to coverage issues, and static analysis of R remains an open problem.

\begin{lstlisting}[H,caption={Unnecessary use of \eval},label=lst:unnecessary]
 PerformanceAnalytics::chart.QQPlot <- function (d="norm",dp,...) {
   q.f <- eval(parse(text=paste0("q",d)))
   z <- NULL
   eval(parse(text=paste0("z<-q.f(",dp,",...)")))
   ...
 }
\end{lstlisting}\medskip

@@

\begin{lstlisting}[H]
 q.f <- get(paste0("q",d))
 z <- q.f(dp, ...)
\end{lstlisting}

\paragraph{Eval alternatives}

There are alternative implementations of \eval. The \k{lazyeval} package
provides \k{lazy} and \k{lazy_eval} as safer variants for the built-in
\k{substitute} and \k{eval} functions. The main differences are
that the \k{lazy} function captures not only the expression, but also the
environment associated with a function argument, and that it follows promises
across function invocations. This helps to avoid scoping bugs, as shown in the
example bellow:

\begin{figure}[H]
  \begin{minipage}{.48\textwidth}
    \begin{lstlisting}[title={Use of R \eval},label=lst:lazyeval]
 filter <- function(df, cond) {
   conf <- substitute(cond)
   r <- eval(cond, df, parent.frame())
   df[r, ]
 }

 f <- function(...) {
   x <- 1
   filter(flights, ...)
 }

 x <- 2020
 f(year > x) # uses wrongly 1 for x
    \end{lstlisting}
  \end{minipage}
  \begin{minipage}{.48\textwidth}
    \begin{lstlisting}[title={Use of \k{lazyeval}},label=lst:lazyeval]
 filter <- function(df, cond) {
   cond <- lazy(cond)
   r <- lazy_eval(cond, df)
   df[r, ]
 }

 f <- function(...) {
   x <- 1
   filter(flights, ...)
 }

 x <- 2020
 f(year > x) # uses correctly 2020 for x
\end{lstlisting}
\end{minipage}
\end{figure}

The \k{filter} function selects rows from \k{df} that match a given condition
passed in \k{cond}. However, the implementation using the built-in R \eval has a
scoping issue since it does not correctly capture the proper environment
associated with the condition.\footnote{This is a simplified version of the
  built-in \texttt{\scriptsize subset} function which suffers from this exact
problem.} The \k{lazyeval} version does not manifest the issue as it properly
captures the correct environment.

The tidyverse libraries\footnote{An opinionated collection of R packages
designed for data science. It consists of some of the most popular packages.}
include their own implementation of \eval called
\k{rlang::eval\_tidy}~\cite{tidyverse}, which departs from \eval in two ways.
First, it supports the evaluation of quosures, custom objects used for
metaprogramming that bundle expressions with an environment. The \k{eval\_tidy}
function accepts a data mask argument, a set of bindings such as a data frame
or list, which takes precedence over the environment. Effects such as
assignments happen in the data mask, and expressions such as \k{return()} do
not work since the data mask does not correspond to a frame on the call stack.
